\documentclass{report}
%%% Import Packages %%%
\usepackage [a4paper, portrait, margin=1in]{geometry}
\usepackage{adjustbox}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage[T1]{fontenc}
%%%

%%% Header and Footer Text %%%
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{e-store}
\fancyhead[RE,LO]{Charter}
\fancyfoot[CE,CO]{\leftmark}
\fancyfoot[LE,RO]{\thepage}

\renewcommand{\headrulewidth}{2pt}
\renewcommand{\footrulewidth}{1pt}
%%% 

%%% Typesetting %%%
\linespread{1.20}
%%%

\begin{document}
\title{\textbf{Estore Documentation} \\ 
}
\author{
\normalsize
Ebarle, Roselle \\
Maglasang, Catherine \\
Yee, Mar Rynner \\
Esin, Dexter \\
}


\pagenumbering {gobble}
\maketitle
\tableofcontents
\newpage
\pagenumbering {arabic}

\chapter{Charter}
\section{Abstract}
e-store is an open-source, python-based ecommerce platform for online merchants. It provides the power to grow your web business, reach more customers and sell more products and services. It enables businesses to experience an integrated workflow for their business - Accounting, Inventory and Order Management and Customer Service under one platform. 

\section{Vision}
To be the most trusted integrated e-commerce platform for merchants

\section{Mission}
To develop a platform with utmost regards in security and customer satisfaction in the e-commerce industry

\section{Objectives}
\begin{enumerate}
\item Within 2 weeks after project initiation, the developers will already have a design and plan for the project's interface and architecture. The developers will come up with an initial product backlog and be able to commence the first sprint planning.
\item Within 7 weeks after planning, the team will finish the first sprint. And come up with 50 \% of the planned major features and interface. 
	\begin{itemize}
	\item Within 1 week, the admin dashboard interface and functionalities such as adding products is created.
	\item Then, Within 1 week, the customers are now able to login and register in the site.
	\item Then, Within 1 week, the customers can now view the products and the product detail page.
	\item Then, Within 2 weeks, the search feature is already implemented.  
	\item Then, Within 2 weeks, the add to cart functionality is created. 
	\end{itemize}
\item Within 5 weeks after the first sprint, the second sprint will be completed. The system will complete at least 90 \% of its proposed major features. 
	\begin{itemize}
	\item Within 1 week, the customers are now able to add product feedback (or ratings)
	\item Then, within 1 week, the social sharing, add to favorites features are now implemented.
	\item Then, within 1 week, the related products section and contact admin features are now implemented. 	
	\item Then, within 1 week, the recommendation feature is already added.
	\item Then, within 1 week, the currency converter feature is already added.  
	\end{itemize}
\item Within 1 week after the second sprint the main features decided by the team would be completed and tested correctly by the client. 
\end{enumerate}

\section{Principles}
Secure Transactions
Scalability and Speed

\section{Features}
\begin{enumerate}
\item Admin Logout
\item Admin Login
\item Customer Login
\item Customer Logout
\item Customer Signin \\ \\
\textbf{Customer Dashboard}
\item View my Orders
\item View my Wishlist
\item View my Reviews
\item Re-order items
\item Update Settings \\ \\
\textbf{Admin Dashboard}
\item Add Staff
\item Update Staff
\item Revoke Staff Access
\item Add Order
\item View Customer Orders
\item Add Products
\item View Products
\item Add Category
\item View Category
\item Add Supplier
\item View Supplier 
\item Add Customer
\item View Customers
\item View Sales Report
\item Add Promotion 
\item Add Static page
\item Add Content Block \\ \\
\textbf{Store Catalog / Store Page}
\item Filter Products
\item Product Social Sharing
\item Add to Wishlist
\item Search Product
\item Add Feedback
\item View Related Products
\item Customer Behaviour Tracking
\item Abandoned Cart
\item Checkout Payment
\item Automated Fulfillment
\end{enumerate}

\section{Business Rules}
\begin{enumerate}
\item When signing up, the customer can only use the alphanumeric characters and the password has a required field of 6-22 valid characters
\item The email/username is unique to every account that is recorded in the database
\item When signing up, the information inputted must be complete such as the email/username, password, contact info, and confirm password
\item When filling up the form, the password and the confirm password must be the same
\item The username and password must be recorded on the database for the customer to be logged in
\item The customer and admin has different access rights
\item The customers not logged in will not be able to checkout their cart
\item When the admin adds a product all the information of the product must be complete
\item feedback for a product is limited to only 500 characters
\end{enumerate}

\chapter{Stories}
\section{Roles}
Customer - The customer browses and interacts within the store page \\ \\
Admin - The admin is responsible in handling and managing orders and inventory in the admin dashboard. 

\section{Role Attributes}
Customer: \\
Frequency of Use: Everyday \\
Domain Expertise: Moderate \\
Computer Expertise: Good \\
General Goals: Browse and buy products he need in the site. \\ \\
Admin: \\
Frequency of Use: Everyday \\
Domain Expertise: Excellent \\
Computer Expertise: Excellent \\
General Goals: Manage orders and inventory \\

\section{Persona}
\subsection{User}
Akira loves shopping. Akira loves buying some rock magazines, manga, novels, gadgets, accessories and even the latest ones. Sometimes Akira is having a hard time dealing laziness because Akira doesn’t like to go to a mall for shopping but he wants to buy some products from a mall. Akira found S-List. After finding S-List, Akira found out that buying products online is easier and Akira found out that there is no need to go to a mall for shopping.

\subsection{Admin}
Jane was a blogger who likes shopping. The owner of the website hired her to manage the website. Her job is to add a product, make a product be featured in the home page, add new categories for the products, update the information of a product, and delete a product

\section{User Stories}
\begin{enumerate}
\item As an admin, I want to login to the website
\item As an admin, I want to be able to logout of the website
\item As a customer, I want to login to the website
\item As a customer, I want to be able to logout of the website
\item As a customer, I want to register to the website
\item As the customer, I want to be able to view the orders i've made so that I could track the status of my order. 
\item As the customer, I want to view the items in my wishlist
\item As the customer, I want to view the reviews I submitted for the products I bought
\item As the customer, I want to be able to re-order products i've ordered in the past
\item As the customer, I want to update my profile settings
\item As an admin, I want to view the orders of my customers
\item As an admin, I want to add products
\item As an admin, I want to view all the products
\item As an admin, I want to view all my customers
\item As an admin, I want to view my sales report
\item As a customer, I want to filter the product by its brand and its price
\item As a customer, I want to share the product to social media sites
\item As a customer, I want to add the product to my wishlist
\item As a customer I want to search a particular product 
\item As a customer, I want to add a product feedback
\item As a customer, I want to view the related products
\end{enumerate}

\chapter{Use Cases}
\begin{tabular}{ l l }
\textbf{Use Case Element} & \textbf{Description} \\
ID 					& 1 \\
Name 				& Get all products \\
Description 			& Get all product details from database \\ 
Primary Actors 		& Admin \\
Pre - Condition 		& User is logged in the system and has administrator privileges \\ 
Post - Condition 	& The product details are outputted in the product table in admin dashboard \\ 
Main Course			& 1. The user accesses the product page in admin dashboard \\
 					& 2. The client fetches the api resource url ‘/api/v1/products/’ \\
 					& 3. The api backend returns a json to the client containing the product details \\ 
 					& 4. The client processes the json result from the api backend and outputs it in \\
 					& 5. the product table \\
 					& 6. The user sees the product and product details in the product table \\
Alternate Flows		& \\
Exceptions 			& 3a. The api returns an empty array of products\\ 
					& \qquad 1. The client will output a message saying ‘No products found’ \\
					& \qquad 2. The user sees the message that no products are found \\ \\
ID 					& 2 \\
Name 				& Get Single Product\\
Description 			& Get the details of a single product \\ 
Primary Actors 		& Admin\\
Pre - Condition 		& The user is logged in and the user has administrator privileges \\ 
Post - Condition 	& The user should see the details of the product in the product details page \\ 
Main Course			& 1. The user accesses the product page \\
					& 2. The user clicks on the product id he wants to view \\
					& 3. The client fetches the api resource url ‘/api/v1/products/2’ \\ 
					& 4. The api backend returns a json to the client containing the product details \\ 
					& 5. The client processes the json result from the api backend and outputs \\
					& it in the table \\
					& 6. The user sees the product details in the product detail page \\
Alternate Flows		& \\
Exceptions 			& 4a. The api backend returns no existing product \\
					& \qquad 1. The client outputs a message saying that the product doesn’t exist \\

\end{tabular}
\newpage

\begin{tabular}{ l l }					
ID 					& 3 \\
Name 				& Create a Product\\
Description 			& Create a product in inventory / catalogue \\ 
Primary Actors 		& Admin \\
Pre - Condition 		& The user is logged in and the user has administrator privileges \\ 
Post - Condition 	& The product should appear in the product table \\ 
Main Course			& 1. The user accesses the product page \\
					& 2. The user clicks on the add product button \\
					& 3. The user fills up the form in add new product page \\
					& 4. The user clicks on submit \\
					& 5. The client processes the form input and values \\
					& 6. The client posts to the product resource url ‘/api/v1/products/’ and \\ 
					& \quad \thinspace adds the form inputs as a data parameter in json form \\
					& 7. The api backend processes the post request from the client \\
					& 8. The api saves the new product in database \\
					& 9. The client redirects to the product page \\
					& 10. The user sees the new product in the product table \\
Alternate Flows		& \\
Exceptions 			& 9a. The product already exists in the database \\
					& \qquad 1. The api returns the error to the client \\
					& \qquad 2. A message in the form should appear indicating that the product \\ 
					& \qquad \quad \thinspace already exists \\ \\
ID 					& 4 \\
Name 				& Update a Product\\
Description 			& Update a product’s details in inventory / catalogue \\ 
Primary Actors 		& Admin \\
Pre - Condition 		& The user is logged in and the user has administrator privileges \\ 
Post - Condition 	& The new product details should appear in the product table \\ 
Main Course			& 1. The user accesses the product page \\
					& 2. The user clicks on the edit button in the product row \\
					& 3. The system redirects the user to the Edit Product Page \\
					& 3. The user re-fills up the form and update the details as needed \\
					& 4. The user clicks on submit \\
					& 5. The client processes the form input and values \\
					& 6. The client sends a put request to the product resource url \\ 
					& ‘/api/v1/products/’  and adds the form inputs as a data parameter \\ 
					& in json form \\
					& 7. The api backend processes the ‘put’ request from the client \\ 
					& 8. The api updates the product in database \\
					& 9. The user is redirected to the product page \\
					& 10. The user sees the new product details in the product table \\
Alternate Flows		& \\
Exceptions 			& \\

\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 					& 5 \\
Name 				& Add a Supplier \\
Description 			& Add a supplier for the product \\ 
Primary Actors 		& Admin\\
Pre - Condition 		& The supplier to be added has a name, address, phone number, fax and email. \\ 
Post - Condition 	& The supplier is added in the database and can be viewed on the supplier \\ 
					& list page \\ 
Main Course			& 1. The admin is on the  supplier page. \\
					& 2. The admin Clicks on the add Supplier tab and is redirected to the \\ 
					& add supplier form \\
					& 3. The admin enters the name, address, phone number, fax, and email of \\
					& the supplier \\
					& 4. The Admin clicks on the submit button \\
					& 5. The supplier is added and is saved in the database \\
					& 6. There is a pop up message that says “the supplier was successfully added” \\
					& 7. Exit \\
Alternate Flows		& \\
Exceptions 			& 4.a There is a blank input box. \\
					& \qquad 1.1 The admin will redirected to the add supplier form \\
					& \qquad 1.2 There is a message that tells the admin to fill in all input boxes \\
					& \qquad 1.3 Back to step 4 \\ 
					& 4b: Supplier already exists \\
					& \qquad 2.1 There is a pop up message that says “Supplier already exists” \\	
					& \qquad 2.1 Back to step 3. \\ \\
ID 					& 6 \\
Name 				& Update Supplier \\
Description 			& Update Supplier Information \\ 
Primary Actors 		& Admin \\
Pre - Condition 		& \\ 
Post - Condition 	& \\ 
Main Course			& 1. The admin is on the  supplier page. \\
					& 2. The admin Clicks on the update Supplier button and is redirected to the \\ 
					& \quad \thinspace update supplier form \\
					& 3. The admin enters the name, address, phone number, fax, and email \\ 
					& \quad \thinspace of the supplier \\
					& 4. The Admin clicks on the submit button \\
					& 5. The supplier is updated and is saved in the database \\
					& 6. There is a pop up message that says “the supplier was successfully \\ 
					& \quad \thinspace updated” \\
					& 7. Exit \\
Alternate Flows		& \\
Exceptions 			& 4a There is a blank input box. \\
					& \qquad 1.1 The admin will redirected to the add supplier form \\
					& \qquad 1.2 There is a message that tells the admin to fill in all input boxes \\
					& \qquad 1.3 Back to step 4 \\ \\
\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 					& 7 \\
Name 				& View all Supplier \\
Description 			& View all supplier on the list \\ 
Primary Actors 		& Admin \\
Pre - Condition 		& The admin is on the Admin dashboard page \\ 
Post - Condition 	& The list of all suppliers is shown \\ 
Main Course			& 1. The admin clicks on the supplier tab and will then be redirected \\ 
					& \quad \thinspace to the  supplier page. \\
					& 2. The admin Clicks on the view Supplier tab and is redirected \\ 
					& \quad \thinspace to the supplier list page \\
					& 3. The Supplier list is shown \\
					& 4. Exit \\
Alternate Flows		& \\
Exceptions 			& \\ \\
ID 					& 8 \\
Name 				& Add Order \\
Description 			& Add Customer Order \\ 
Primary Actors 		& Admin \\
Pre - Condition 		& The order to be added has a customer id, payment id, transaction date, shipping date \\
					& \quad \thinspace and time stamp. \\ 
Post - Condition 	& The order is added in the database and can be viewed on the order list page \\ 
Main Course			& 1. The admin is on the  order page. \\
					& 2. The admin Clicks on the add order tab and is redirected to the add order form \\
					& 3. The admin enters the customer id, payment id, transaction date, shipping date \\
					& \quad \thinspace and time stamp of the order \\
					& 4. The Admin clicks on the submit button \\
					& 5. The order is added and is saved in the database \\
					& 6. There is a pop up message that says “the order was successfully added” \\
					& 7. Exit\\
Alternate Flows		& \\
Exceptions 			& 4a There is a blank input box. \\
					& \qquad 1.1 The admin will redirected to the add order form \\
					& \qquad 1.2 There is a message that tells the admin to fill in all input boxes \\
					& \qquad 1.3 Back to step 4 \\
					& 4b: Order already exists \\
					& \qquad 2.1 There is a pop up message that says “Order already exists” \\	
					& \qquad 2.1 Back to step 3. \\
\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 					& 9 \\
Name 				& View all Orders \\
Description 			& View all orders on the list \\ 
Primary Actors 		& Admin \\
Pre - Condition 		& The admin is on the Admin dashboard page \\ 
Post - Condition 	& The list of all orders is shown \\ 
Main Course			& 1. The admin clicks on the order tab and will then be redirected to \\ 
					& \quad \thinspace the  order page. \\
					& 2. The admin Clicks on the view orders tab and is redirected to the \\ 
					& \quad \thinspace supplier list page \\
					& 3. The Supplier list is shown \\
					& 4. Exit \\
Alternate Flows		& \\
Exceptions 			& \\ \\
ID 					& 10 \\
Name 				& Add Order Item \\
Description 			& Add an Order Item\\ 
Primary Actors 		& Admin \\
Pre - Condition 		& The order item to be added has an order id, product id, unit price, \\ 
					& discount and quantity. \\ 
Post - Condition 	& The order item is added in the database and can be viewed on the \\
					& order item list page \\ 
Main Course			& 1. The admin is on the order page. \\
					& 2. The admin Clicks on the add order item button and is redirected to \\ 
					& \quad \thinspace the add order item form \\
					& 3. The admin enters the order id, product id, unit price, discount and quantity \\
					& 4. The admin clicks on the submit button \\
					& 5. The order item is added and is saved in the database \\
					& 6. There is a pop up message that says “the order item was successfully added” \\
					& 7. Exit \\
Alternate Flows		& \\
Exceptions 			& 4a. There is a blank input box.\\
					& \qquad 1.1 	The admin will redirected to the add supplier form \\
					& \qquad 1.2 	There is a message that tells the admin to fill in all input boxes \\
					& \qquad 1.3 	Back to step 4 \\
					& 4b: Order Item is already exists \\
					& \qquad 2.1 There is a pop up message that says “Order item already exists” \\	
					& \qquad 2.1 Back to step 3. \\ \\

\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 					& 11 \\
Name 				& Add Cart \\
Description 			& Add new Cart \\ 
Primary Actors 		& Admin \\
Pre - Condition 		& The cart has a session id, date created and customer id \\ 
Post - Condition 	& The new cart is added and saved in the database and can be viewed on the cart page \\ 
Main Course			& 1. The admin is on the cart page \\
					& 2. The admin clicks on the add cart tab and is redirected on the add cart form page \\
					& 3. The admin inputs the cart session id, date created and customer id. \\
					& 4. The admin clicks on the submit button \\
					& 5. The new cart is added and saved in the database and can be viewed on the cart page \\
					& 6. Exit \\ \\
Alternate Flows		& \\
Exceptions 			& 4a. There is a blank input box. \\
					& \qquad 1.1 	The admin will redirected to the add supplier form \\
					& \qquad 1.2 	There is a message that tells the admin to fill in all input boxes\\
					& \qquad 1.3 	Back to step 4 \\
ID 					& 12 \\
Name 				& View All Carts \\
Description 			& View All Carts on the List \\ 
Primary Actors 		& Admin \\
Pre - Condition 		& The admin is on the Admin dashboard page \\ 
Post - Condition 	& The list of all carts is shown \\ 
Main Course			& 1. The admin clicks on the cart tab and will then be redirected to the  cart page. \\
					& 2. The admin Clicks on the view carts tab and is redirected to the cart list page \\
					& 3. The cart list is shown \\
					& 4. Exit \\
Alternate Flows		& \\
Exceptions 			& \\ \\
ID 					& 13 \\
Name 				& View Wishlist \\
Description 			& View Products that was added in the Wishlist\\ 
Primary Actors 		& Customer \\
Pre - Condition 		& The customer is logged in and is in the customer dashboard \\ 
Post - Condition 	& The customer will be able to view the products he/she added to wishlist \\ 
Main Course			& 1. The use case begins when the customer logs in the customer dashboard. \\
					& 2. The user clicks on “My Wishlist” link in the navigation section. \\
					& 3. The system displays all items in the wishlist of the user. \\
					& 4. The user sees all items he added in wishlist. \\
					& 5. The use case exits.\\
Alternate Flows		& \\
Exceptions 			& \\

\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 					& 14 \\
Name 				& Add to wishlist \\
Description 			& Adding a product to the customer’s wishlist \\ 
Primary Actors 		& Customer \\
Pre - Condition 		& The customer is logged in and is in the customer dashboard \\ 
Post - Condition 	& The specified product will be added to the costumer’s wishlist \\ 
Main Course			& 1. The customer clicks the heart icon on the product page. \\ 
     				& 2. The specified product will be reflected on the customer's wishlist. \\
     				& 3. The use case exits.\\
Alternate Flows		& \\
Exceptions 			& 2a. If the specified product is already in the customer’s wishlist \\
					& \qquad 1. it shows an error message \\
					& \qquad 2. Exit. \\ \\
ID 					& 15 \\
Name 				& View Categories \\
Description 			& View all Categories\\ 
Primary Actors 		& Customer \\
Pre - Condition 		& The customer is logged in and is in the customer dashboard \\ 
Post - Condition 	& The customer will be able to view all categories \\ 
Main Course			& 1. The use case begins when the customer logs in the customer dashboard. \\
					& 2. The user clicks on “Categories” link in the navigation section. \\
					& 3. The system displays all categories. \\
					& 4. The user sees all the categories. \\
					& 5. The user clicks the category button. \\
					& 6. The user sees the product/s that is under a certain category. \\
					& 7. The use case exits. \\
Alternate Flows		& \\
Exceptions 			& \\ \\
ID 					& 16 \\
Name 				& Add Category \\
Description 			& Add a new Category \\ 
Primary Actors 		& Admin \\
Pre - Condition 		& The admin is in the admin dashboard \\ 
Post - Condition 	& The category will be added in the category list \\ 
Main Course			& 1. The admin is in the admin dashboard. \\
					& 2. The admin clicks the add category button and will be displayed in the category page. \\
					& 3. The admin clicks on the add button. \\
    					& 4. The category is added. \\
Alternate Flows		& \\
Exceptions 			& 3a. If the category exists \\
					& \qquad 1. it show an error message \\ 
					& \qquad 2. Exit.\\ \\
\end{tabular}

\chapter{Test Cases}
\begin{tabular}{ l l }
ID 			& 1 \\
Scenario		& Add Attribute\\
Given 		& I have the following data \\
			& | attribute\_name | validation | \\
      		& | default | default | \\
When 		& I save the data \\
Then 		& I get a "201" response \\
And			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\ \\
ID 			& 2 \\
Scenario		& Update Attribute \\
Given 		& I have a resource with the id "1" \\
And 			& I want to update its data to the following data \\
      		& | attribute\_name | validation | \\
      		& | default | default | \\
When 		& I update the data \\
Then 		& I get a "200" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\ \\
ID 			& 3 \\
Scenario		& Create Cart Item \\
Given 		& I have the following data \\
     		& | id | cart\_id | product\_id | quantity   | time\_stamp |\\
     		& | 1  | 1       | 1          | 1          | 2016-03-15 11:49:17|\\
When 		& I Post the cart item to resource url  '/api/v1/carts/1/items/' \\
Then 		& I should get response '200' \\
And 			& I should get "status" 'ok'\\
And 			& I should get "message" 'OK'

\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 			& 4 \\
Scenario		& Create duplicate cart item \\
Given 		& I have the following data \\
     		& | id | cart\_id | product\_id | quantity   | time\_stamp |\\
     		& | 1  | 1       | 1          | 1          | 2016-03-15 11:49:17|\\
When 		& I Post the cart item to resource url  '/api/v1/carts/1/items/' \\
Then 		& I should get response '200' \\
And 			& I should get "status" 'ok'\\
And 			& I should get "message" 'ID EXISTS' \\ \\
ID 			& 5 \\
Scenario		& Get cart item \\
Given 		& cart item '1' is in the system \\
When 		& I retrieve the cart item '1' \\
Then 		& I should get response '200' \\
AND 			& the following cart item details are returned: \\
			& | cart\_id | product\_id | quantity   | time\_stamp         | \\
     		& | 1       | 1          | 1          | 2016-03-15 11:49:17| \\ \\
ID 			& 6 \\
Scenario		& Get a cart item that doesn't exist \\
Given 		& I retrieve the cart item '2' \\
When 		& i retrieve JSON result \\
Then 		& I should get response '200' \\
And 			& I should get "status" 'ok' \\
And 			& I should get a message containing 'No entries found' \\
And 			& it should have a field "count" 0 \\
And 			& it should have an empty field " entries " \\ \\
ID 			& 7 \\
Scenario		& Create cart \\
Given 		& I have the following data \\
    			& |id | session\_id | date\_created| customer\_id| is\_active | \\
    			& |1  | 1          | 2016-03-15  | 1          | True      |\\
When 		& I Post the cart to resource url  '/api/v1/carts/' \\
Then 		& I should get response '200' \\
And 			& I should get "status" 'ok'\\
And 			& I should get "message" 'OK' \\ \\
ID 			& 8 \\
Scenario		& Create Duplicate Cart \\
Given 		& I have the following data \\
    			& |id | session\_id | date\_created| customer\_id| is\_active | \\
 			& |1  | 1          | 2016-03-15  | 1          | True      |\\
When 		& I Post the cart to resource\_url  '/api/v1/carts/' \\
Then 		& I should have a status code '200' \\
And			& I should get a status 'ok' \\
And 			& I should get a message 'ID EXISTS' 
\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 			& 9 \\
Scenario		& Get cart \\
Given 		& cart '1' is in the system \\
When 		& I retrieve the cart '1' \\
Then 		& I should have a status code '200' \\
And 			& the following cart details are returned : \\
		    & | session\_id | date\_created| customer\_id| is\_active | \\
      		& | 1          | 2016-03-15  | 1          | True      | \\ \\
ID 			& 10 \\
Scenario		& Get a Cart that Doesn't Exist \\
Given 		& I retrieve the cart '2' \\
When 		& i retrieve a JSON result \\
Then 		& I should have a status code '200' \\
And 			& I should get a status 'ok' \\
And 			& it should  have a field "message" 'No entries found' \\
And 			& it should  have a field "count" 0 \\
And 			& it should  have an empty field " entries " \\
ID 			& 11 \\
Scenario		& Get Customer \\
Given 		& customer id '1' is in the system \\
When 		& I retrieve the customer id '1' \\
Then 		& I get the customer '200' response \\
And 			& the following customer details are shown: \\
 			& | id | first\_name | last\_name | address | city | state | postal\_code | country | phone | \\
 			& email | user\_id | billing\_address | shipping\_address | date\_created | \\
    			& | 1 | first1 | last1 | address1 | city1 | state1 | postalcode1 | country1 | phone1 | test@estore.com | \\
    			& 1 | baddress1 | saddress1 | 2016-03-11 11:49:17 | \\
ID 			& 12 \\
Scenario		& Get Customer not in the Database \\
Given 		& I access the customer url '/api/v1/customers/2/' \\
When 		& I retrieve the customer JSON result \\
Then 		& I get the customer '200' response \\
And			& it should have a customer field 'status' containing 'ok' \\
And 			& it should have a customer field 'message' containing 'No entries found' \\
And 			& it should have a customer field 'count' containing '0' \\
And 			& it should have an empty customer field 'entries' \\
ID 			& 13 \\
Scenario		& Create Customer \\
Given 		& I have the following data \\
   			& | id | first\_name | last\_name | address | city | state | postal\_code | country | phone | \\
   			&  email | user\_id | billing\_address | shipping\_address | date\_created | \\
  			& | 9 | first9 | last9 | address9 | city9 | state9 | postalcode9 | country9 | phone9 | \\
  			& test9@estore.com | 9 | baddress9 | saddress9 | 2016-03-11 11:49:17 | \\
When 		& I POST to the customer url '/api/v1/customers/' \\
Then 		& I get the create customer '201' response \\
And			& I should get a customer field 'status' containing 'ok' \\
And 			& I should get a customer field 'message' containing 'ok' \\
\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 			& 14 \\
Scenario		& Create Duplicate Customer \\
Given 		& I have the following data \\
    			& | id | first\_name | last\_name | address | city | state | postal\_code | country | phone | \\
    			& email | user\_id | billing\_address | shipping\_address | date\_created | \\
   			& | 9 | first9 | last9 | address9 | city9 | state9 | postalcode9 | country9 | phone9 | \\
   			& test9@estore.com | 9 | baddress9 | saddress9 | 2016-03-11 11:49:17 | \\
When 		& I POST to the customer url '/api/v1/customers/' \\
Then 		& I get the create customer '201' response \\
And 			& I should get a customer field 'status' containing 'ok' \\
And 			& I should get a customer field 'message' containing 'CUSTOMER EXISTS' \\ \\
ID 			& 15 \\
Scenario		& Create Customer with Missing Details \\
Given 		& I have the following data \\
  			& | id | first\_name | last\_name | address | city | state | postal\_code | country | phone | \\
    			& email | user\_id | billing\_address | shipping\_address | date\_created | \\
		    & | 10 |  | | address9 | city9 | state9 | | country9 | phone9 |  | 9 |  |  | 2016-03-11 11:49:17 |\\
When 		& I POST to the customer url '/api/v1/customers/' \\
Then 		& I get the create customer '201' response \\
And 			& I should get a customer field 'status' containing 'ok' \\
And 			& I should get a customer field 'message' containing 'error' \\ \\
ID 			& 16\\
Scenario		& Add Image \\
Given 		& I have the following data \\
      		& | item\_id | image\_url  | caption | \\
      		& | 1       | google.com | hi      |\\
When 		& I save the data \\
Then 		& I get a "201" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok"\\ \\
ID 			& 17\\
Scenario		& Update Image\\
Given 		& I have a resource with the id "1" \\
And 			& I want to update its data to the following data \\
      		& | image\_id | item\_id | image\_url  | caption | \\
      		& | 1        | 1       | google.com | hi      | \\
When 		& I update the data\\
Then 		& I get a "200" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\
\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 			& 18\\
Scenario		& Add Item Attribute \\
Given 		& I have the following data \\
	      	& | attribute\_id | item\_id | attribute\_value | \\
      		& | 1            | 1       | Default         | \\
When 		& I save the data \\
Then 		& I get a "201" response \\
And 			& I get a field "status" containing "ok" \\ 
And 			& I get a field "message" containing "ok" \\ \\
ID 			& 19\\
Scenario		& Update Item Attribute \\
Given 		& I have a resource with the id "1" \\
And 			& I want to update its data to the following data \\
      		& | attribute\_id | item\_id | attribute\_value | \\
      		& | 1            | 1       | New Default     | \\
When 		& I update the data \\
Then 		& I get a "200" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\ \\
ID 			& 20\\
Scenario		& Add Item Variation \\
Given 		& I have the following data \\
	      	& | item\_id | option\_id | stock\_on\_hand | unit\_cost | re\_order\_level | re\_order\_quantity | is\_active | \\
      		& | 1       | 1         | 100.00        | 10.00     | 100.00         | 100.00            | true      | \\
When 		& I save the data \\
Then 		& I get a "201" response \\
And			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\ \\
ID 			& 21 \\
Scenario		& Update Item Variation \\
Given 		& I have a resource with the id "1" \\
And			& I want to update its data to the following data \\
      		& | item\_id | option\_id | stock\_on\_hand | unit\_cost | re\_order\_level | re\_order\_quantity | is\_active | \\
      		& | 1       | 1         | 100.00        | 10.00     | 100.00         | 100.00            | true      | \\
When 		& I update the data \\
Then 		& I get a "200" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\
\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 			& 22\\
Scenario		& Add Item \\
Given 		& I have the following data \\
	      	& | name | description | date\_added     | date\_updated   | is\_active | \\
      		& | name | description | 2001-1-1 1:1:1 | 2001-1-1 1:1:1 | true      | \\
When 		& I save the data \\
Then 		& I get a "201" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\ \\
ID 			& 23\\
Scenario		& Update Item \\
Given 		& I have a resource with the id "1" \\
And 			& I want to update its data to the following data \\
      		& | name | description | date\_added     | date\_updated   | is\_active | \\
      		& | name | description | 2001-1-1 1:1:1 | 2001-1-1 1:1:1 | true      | \\
When 		& I update the data \\
Then 		& I get a "200" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\ \\
ID 			& 24\\
Scenario		& Add Location \\
Given 		& I have the following data \\
      		& | location\_name | \\
      		& | name      |\\
When 		&  I save the data \\
Then 		& I get a "201" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\ \\
ID 			& 25\\
Scenario		& Update Location \\
Given 		& I have a resource with the id "1" \\
And 			& I want to update its data to the following data \\
      		& | location\_name | \\
      		& | new name      | \\
When 		& I update the data \\
Then 		& I get a "200" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\
\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 			& 26\\
Scenario		& Add Option Group \\
Given 		& I have the following data \\
	      	& | option\_group\_name | \\
      		& | default      | \\ 
When 		& I save the data \\
Then 		& I get a "201" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\ \\
ID 			& 27\\
Scenario		& Update Option Group \\
Given 		& I have a resource with the id "1" \\
And 			& I want to update its data to the following data \\
      		& | option\_group\_name | \\
	      	& | default      | \\
When 		& I update the data \\
Then 		& I get a "200" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\ \\
ID 			& 28\\
Scenario		& Add Option \\
Given 		& I have the following data \\
	      	& | option\_group\_id | option\_value | \\
      		& | 1               | default      | \\
When 		& I save the data \\
Then 		& I get a "201" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\ \\
ID 			& 29\\
Scenario		& Update Option \\
Given 		& I have a resource with the id "1" \\
And 			& I want to update its data to the following data \\
      		& | option\_group\_id | option\_value | \\
      		& | 1               | default      | \\
When 		& I update the data \\
Then 		& I get a "200" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" 
\end{tabular}
\newpage


\begin{tabular}{ l l }
ID 			& 30\\
Scenario		& Create order item \\
Given 		& I have the following data \\
	    		& | id | order\_id | item\_id | unit\_price | discount | quantity | \\
    			& | 1  | 1        | 1          | 100.0      | 0.1      | 20       |\\
When 		& I Post the order item to resource\_url  '/api/v1/orders/1/items/' \\
Then 		& I should have a response '200' \\
And 			& I should have a "status" containing 'ok' \\
And 			& I should have a "message" containing 'OK' \\ \\
ID 			& 31\\
Scenario		& Create a duplicate order item \\
Given 		& I have the following data \\ 
     		& | id | order\_id | item\_id | unit\_price | discount | quantity | \\
     		& | 1  | 1        | 1          | 100.0      | 0.1      | 20       |\\
When 		& I Post the order item to resource\_url  '/api/v1/orders/1/items/' \\
Then 		& I should have a response '200' \\
And 			& I should have a "status" containing 'ok' \\
And 			& I should have a "message" containing 'ID EXISTS' \\ \\
ID 			& 32\\
Scenario		& Create order item with incomplete details \\
Given 		& I have the following order item details \\
     		& | id | order\_id | item\_id | unit\_price | discount | quantity | \\
     		& | 2| 1 | | 100.00 | 0.1      | 20       | \\
When 		& I Post the order item to resource\_url  '/api/v1/order\_items/' \\
Then 		& I should have a response '200' \\
And 			& I should have a "status" containing 'ok' \\
And 			& I should have a "message" containing 'error'\\ \\
ID 			& 33\\
Scenario		& Get an order item \\
Given 		& order item id '1' is in the system \\
When 		& I retrieve the order item '1' \\
Then 		& I should have a response '200' \\
And 			& the following order item details are returned: \\
    			& | id | order\_id | item\_id | unit\_price | discount | quantity | \\
    			& | 1 | 1        | 1          | 100.0      | 0.1      | 20       |
\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 			& 34\\
Scenario		& Get an order item that doesn't exist\\
Given 		& I retrieve the order item '2'\\
When 		& I retrieve JSON result\\
Then 		& I should have a response '200'\\
And 			& I should have a "status" containing 'ok' \\
And 			& It should have a field "message " 'No entries found' \\
And 			& It should have a field "count " 0 \\
And 			& It should have an empty field " entries " \\ \\
ID 			& 35\\
Scenario		& Create order \\
Given 		& I have the following data \\
    			& |id| customer\_id | payment\_id | transaction\_date | shipping\_date | time\_stamp          | \\
    			& transaction\_status | total | \\
    			& |1 | 1           | 1          | 2016-03-11       | 2016-03-11    | 2016-03-11 11:49:17 | \\
    			& Pending            | 100.0 | \\
When 		& I Post the order to resource\_url  '/api/v1/orders/'\\
Then 		& I should get a status of '200'\\
And 			& I should get a "status" 'ok'\\
And 			& I should get a "message" 'OK'\\ \\
ID 			& 36\\
Scenario		& Create a duplicate order \\
Given 		& I have the following data \\
     		& |id| customer\_id | payment\_id | transaction\_date | shipping\_date | time\_stamp          | \\
     		& transaction\_status | total |\\
     		& |1 | 1           | 1          | 2016-03-11       | 2016-03-11    | 2016-03-11 11:49:17 | \\ 
     		& Pending            | 100.0 |\\
When 		& I Post the order to resource\_url  '/api/v1/orders/' \\
Then 		& I should get a status of '200' \\
And 			& I should get a "status" 'ok' \\
And 			& I should get a "message" 'ID EXISTS'\\ \\
ID 			& 37\\
Scenario		& Create an order with incomplete details \\
Given 		& I have the following data \\
     		& |id| customer\_id | payment\_id | transaction\_date | shipping\_date | time\_stamp          | \\ 
     		& transaction\_status | total | \\
     		& | 2 | 2           | 2          | 2016-03-11       | 2016-03-11    | 2016-03-11 11:49:17 | | 100.0 |\\
When 		& I Post the order to resource\_url  '/api/v1/orders/' \\
Then 		& I should get a status of '200' \\
And 			& I should get a "status" 'ok' \\
And 			& I should get a "message" 'error' \\
\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 			& 38\\
Scenario		& Get Order \\
Given 		& Order id '1' is in the system \\
When 		& I retrieve the order '1' \\
Then 		& I should get a status of '200' \\
And 			& the following orders are returned: \\
    			& | customer\_id | payment\_id | transaction\_date | shipping\_date | time\_stamp          | \\ 
    			& transaction\_status | total | \\
    			& | 1           | 1          | 2016-03-11       | 2016-03-11    | 2016-03-11 11:49:17 | \\ 
    			& Pending            | 100.0 | \\ \\
ID 			& 39\\
Scenario		& Get an order that doesn't exist \\
Given 		& I retrieve the order '2' \\
When 		& I retrieve a  JSON result \\
Then 		& I should get a status of '200' \\3
And 			& I should get a "status" 'ok' \\
And 			& It should  have a "message" "No entries found" \\
And 			& It should  have a field "count" 0 \\
And 			& It should  have an empty field " entries " \\ \\
ID 			& 40\\
Scenario		& Create Supplier \\
Given 		& I have the following data \\
      		& | id | name        | address  | phone   | fax         | email                | is\_active | \\
      		& | 1  | supplier1   | address1 | 221-2277| 063-221-2277| supplier1@estore.com | True      | \\
When 		& I Post the supplier to resource\_url  '/api/v1/suppliers/' \\
Then 		& I should get a response '200' \\
And 			& I should get a "status" containing 'ok' \\
And 			& I should get a "message" containing 'OK' \\ \\
ID 			& 41\\
Scenario		& Create duplicate supplier \\
Given 		& I have the following data \\
       		& | id | name        | address  | phone   | fax         | email                | is\_active | \\
       		& | 1  | supplier1   | address1 | 221-2277| 063-221-2277| supplier1@estore.com | True      | \\
When 		& I Post the supplier to resource\_url  '/api/v1/suppliers/' \\
Then 		& I should get a response '200' \\
And 			& I should get a "status" containing 'ok' \\
And 			& I should get a "message" containing 'SUPPLIER EXISTS' \\
\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 			& 42\\
Scenario		& Create supplier with incomplete details \\
Given 		& I have the following data \\
       		& | id | name | address  | phone   | fax         | email                | is\_active | \\
       		& |  2 | | | | | supplier1@estore.com | True      | \\
When 		& I Post the supplier to resource\_url  '/api/v1/suppliers/'\\
Then 		& I should get a response '200' \\
And 			& I should get a "status" containing 'ok' \\
And 			& I should get a "message" containing 'error' \\ \\
ID 			& 43\\
Scenario		& Get a supplier \\
Given 		& supplier '1' is in the system \\
When 		& I retrieve the supplier '1' \\
Then 		& I should get a response '200' \\
And 			& the following supplier details are returned: \\
    			& | id | name     | address  | phone   | fax         | email                | is\_active | \\
    			& | 1  | supplier1| address1 | 221-2277| 063-221-2277| supplier1@estore.com | True      | \\ \\
ID 			& 44\\
Scenario		& Get a supplier that doesn't exist \\
Given 		& I retrieve the supplier '2' \\
When 		& I get the JSON result \\
Then 		& I should get a response '200' \\
And 			& I should get a "status" containing 'ok' \\
And 			& It should have a field "message" 'No entries found' \\
And 			& It should have a field "count" 0 \\
And 			& It should have an empty field "entries" \\ \\
ID 			& 45\\
Scenario		& Get User \\
Given 		& user id '1' is in the system \\
When 		& I retrieve the user '1' \\
Then 		& I get the '200' response \\
And			& the following user details are shown: \\
      		& | user\_id | username | email            | password | date\_created | is\_admin | \\
      		& | 1       | user9    | user9@estore.com | user9    | 1/1/1 1:1:1  | true     | 
\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 			& 46\\
Scenario		& Get User not in the Database \\
Given 		& I access the user id '2' \\
When 		& I retrieve the user JSON result \\
Then 		& I get the '200' response \\
And 			& it should have a user field 'status' containing 'ok' \\
And 			& it should have a user field 'message' containing 'No entries found' \\
And 			& it should have a user field 'count' containing '0' \\
And 			& it should have an empty field 'entries'\\ \\
ID 			& 47\\
Scenario		& Create User \\
Given 		& I have the following user details: \\
      		& | user\_id | username | email            | password | date\_created | is\_admin | \\
      		& | 1       | user9    | user9@estore.com | user9    | 1/1/1 1:1:1  | true     | \\
When 		& I POST to the user url '/api/v1/users/' \\
Then 		& I get the create '201' response \\
And 			& I should get a user field 'status' containing 'ok' \\
And 			& I should get a user field 'message' containing 'OK' \\
ID 			& 48\\
Scenario		& Create Duplicate User \\
Given 		& I have the following user details: \\ 
      		& | user\_id | username | email            | password | date\_created | is\_admin | \\
      		& | 1       | user9    | user9@estore.com | user9    | 1/1/1 1:1:1  | true     | \\
When 		& I POST to the user url '/api/v1/users/' \\
Then 		& I get the create '201' response \\
And 			& I should get a user field 'status' containing 'ok' \\
And 			& I should get a user field 'message' containing 'USER EXISTS' \\ \\
ID 			& 49\\
Scenario		& Create User with missing Details\\
Given 		& I have the following user details: \\
      		& | user\_id | username | email            | password | date\_created | is\_admin | \\
      		& | 1       | | user9@estore.com | user9    | 1/1/1 1:1:1  | true     | \\
When 		& I POST to the user url '/api/v1/users/' \\
Then 		& I get the create '201' response \\
And 			& I should get a user field 'status' containing 'ok' \\
And 			& I should get a user field 'message' containing 'error' \\
\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 			& 50\\
Scenario		& Create Wishlist Item \\
Given 		& I have the details of wishlist items\\
    			& | wishlist\_item\_id | wishlist\_id | item\_id | time\_stamp |\\
    			& | 2 | 1 | 3 | 2016-04-14 | \\
When 		& I POST to url '/api/v1/wishlist\_items/' the wishlist items \\
Then 		& I should get status code response '200' \\
And 			& I should get 'ok' status \\
And 			& I should get 'OK' message\\ \\
ID 			& 51\\
Scenario		& Create a duplicate wishlist item \\
Given 		& I have the details of wishlist items\\
    			& | wishlist\_item\_id | wishlist\_id | item\_id | time\_stamp | \\
    			& | 2 | 1 | 3 | 2016-04-14 | \\
When 		& I POST to url '/api/v1/wishlist\_items/' the wishlist items \\
Then 		& I should get status code response '200' \\
And 			& I should get 'ok' status \\
And 			& I should get 'ERROR' message for duplication \\ \\
ID 			& 52\\
Scenario		& Create an invalid wishlist item \\
Given 		& I have the details of wishlist items \\
   			& | wishlist\_item\_id | wishlist\_id | item\_id | time\_stamp | \\
    			& | d | x | t | r | \\
When 		& I POST to url '/api/v1/wishlist\_items/' the wishlist items \\
Then 		& I should get status code response '200' \\
And 			& I should get 'error' status for invalid details \\ \\
ID 			& 53\\
Scenario		& Create an incomplete wishlist \\
Given 		& I have the details of wishlist items\\
    			& | wishlist\_item\_id | wishlist\_id | item\_id | time\_stamp |\\
    			& |  | 1 |  | 2016-04-14 | \\
When 		& I POST to url '/api/v1/wishlist/' the wishlist \\
Then 		& I should get status code response '200' \\
And 			& I should get 'ok' status \\
And 			& I should get 'ERROR' message for incomplete details \\
\end{tabular}
\newpage

\begin{tabular}{ l l }
ID 			& 54\\
Scenario		& Get Wishlist Item \\
Given 		& wishlist item '2' is in the system \\
When 		& I retrieve the wishlist '2' \\
Then 		& I should have a status code response '200' \\
And 			& the following details are returned : \\
      		& | wishlist\_item\_id | wishlist\_id | item\_id | time\_stamp | \\
      		& | 2 | 1 | 3 | 2016-04-14 | \\ \\
ID 			& 55\\
Scenario		& Get a wishlist item that doesn't exist \\
Given 		& I retrieve a wishlist item with id '4' \\
When 		& I retrieve the wishlist item JSON result \\
Then 		& I should have a status code response '200' \\
And 			& I should get the status says 'ok' \\
And 			& it should  have a field message saying 'No entries found' \\
And 			& it should  have a field count '0' \\
And 			& it should  have an empty field 'entries' \\ \\
ID 			& 56\\
Scenario		& Add Wishlist \\
Given 		& I have the following data \\
      		& | wishlist\_id | wishlist\_name | \\
      		& | 1      | default      | \\
When 		& I save the data \\
Then 		& I get a "201" response \\ 
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\ \\
ID 			& 57\\
Scenario		& Update Wishlist \\
Given 		& I have a resource with the id "1" \\
And 			& I want to update its data to the following data \\
      		& | wishlist\_id | wishlist\_name | \\
      		& | 1      | default      |\\
When 		& I update the data \\
Then 		& I get a "200" response \\
And 			& I get a field "status" containing "ok" \\
And 			& I get a field "message" containing "ok" \\
\end{tabular}
\newpage


\end{document}
